% !TEX program = pdflatex
% Supplementary material for the AAAI-27 anonymous submission.
% Standalone PDF; does not count toward the 7+2 page limit. Anonymous.
\documentclass[11pt]{article}
\usepackage[a4paper,margin=2.5cm]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{array}
\usepackage[utf8]{inputenc}

\title{Supplementary Material:\\When Does Graph Decomposition Help Multi-Hop QA?\\Performance Boundaries and Sub-Answer Diagnostics}
\author{Anonymous Submission}
\date{}

\begin{document}
\maketitle

This document collects supporting analyses referenced in the main paper. Reviewers are not obligated to examine it; all core claims and evidence appear in the main text.

\section{Qualitative Positioning}

Table~\ref{tab:position} clarifies the scope of GERS-DAG and BiCheck relative to representative reasoning paradigms; it is intended to clarify scope rather than claim full empirical dominance over every family.

\begin{table}[h]
\centering
\caption{Qualitative positioning.}
\label{tab:position}
\small
\begin{tabular}{lccc}
\toprule
Method family & Structure & Execution & Checkable sub-ans. \\
\midrule
CoT & linear text & implicit & no \\
CoT-SC & linear samples & implicit & no \\
ToT / GoT & tree or graph thoughts & search/flexible & state nodes \\
RwG / graph prompts & entity/context graph & prompt-cond. & usually no \\
MoDeGraph-style & dependency prompt & prompt-cond. & entity level \\
GERS-DAG + BiCheck & sub-question DAG & topological & yes, forward/backward \\
\bottomrule
\end{tabular}
\end{table}

\section{Consistency Score Bucket Diagnostics}

Table~\ref{tab:buckets} reports the BiCheck score--correctness breakdown for the released GERS-CV2 configuration (HotpotQA, n=500). AUROC uses EM correctness as the binary label. Although higher score buckets have higher EM accuracy, 156 of the 250 samples with CS=1.0 are still EM-wrong. In the evaluated single-path configuration, this score is computed after the GERS-DAG answer is fixed and is therefore a diagnostic rather than an answer-selection mechanism.

\begin{table}[h]
\centering
\caption{CS--correctness diagnostics (HotpotQA, n=500).}
\label{tab:buckets}
\small
\begin{tabular}{lccc}
\toprule
Score variant or bucket & Samples & EM & F1 \\
\midrule
Old structural CS AUROC & 500 & \multicolumn{2}{c}{AUROC 0.498} \\
BiCheck without confidence aggregation & 500 & \multicolumn{2}{c}{AUROC 0.581} \\
BiCheck with confidence aggregation & 500 & \multicolumn{2}{c}{AUROC 0.589} \\
\midrule
BiCheck, CS $<0.5$ & 75 & 0.200 & 0.278 \\
BiCheck, $0.5\le$ CS $<0.7$ & 86 & 0.244 & 0.333 \\
BiCheck, $0.7\le$ CS $<0.9$ & 85 & 0.247 & 0.375 \\
BiCheck, $0.9\le$ CS $<1.0$ & 4 & 0.000 & 0.167 \\
BiCheck, CS $=1.0$ & 250 & 0.376 & 0.499 \\
\bottomrule
\end{tabular}
\end{table}

\section{Complete LongBench Results}

Table~\ref{tab:longbench} reports all five evaluated LongBench QA subsets. Confidence intervals are paired but are not adjusted for comparisons across datasets and metrics. MuSiQue, NarrativeQA, and 2WikiMQA use only examples for which both methods returned valid outputs.

\begin{table}[h]
\centering
\caption{LongBench paired F1 comparisons.}
\label{tab:longbench}
\small
\begin{tabular}{lrrrll}
\toprule
Subset & $n$ & CoT-SC & GERS-DAG & $\Delta$F1 & 95\% CI \\
\midrule
multifieldqa\_en & 100 & 0.345 & 0.415 & +0.070 & $[+0.007,+0.132]$ \\
musique & 193 & 0.325 & 0.387 & +0.063 & $[+0.001,+0.124]$ \\
narrativeqa & 71 & 0.234 & 0.208 & -0.027 & $[-0.082,+0.026]$ \\
qasper & 200 & 0.272 & 0.290 & +0.018 & $[-0.016,+0.054]$ \\
2wikimqa & 195 & 0.700 & 0.681 & -0.021 & $[-0.076,+0.035]$ \\
\bottomrule
\end{tabular}
\end{table}

\section{Oracle Interventions}

The Oracle configurations are not a cumulative module waterfall. Gold retrieval and gold sub-answers are separate interventions, each conditioned on gold decomposition, and may interact.

\begin{table}[h]
\centering
\caption{MuSiQue 4-hop Oracle interventions (n=200).}
\label{tab:oracle}
\small
\begin{tabular}{lrrr}
\toprule
Configuration & EM & F1 & $\Delta$F1 vs. baseline \\
\midrule
Model-generated pipeline & 0.251 & 0.348 & --- \\
Gold decomposition & 0.335 & 0.439 & +0.091 \\
Gold decomposition + retrieval & 0.407 & 0.514 & +0.166 \\
Gold decomposition + sub-answers & 0.780 & 0.839 & +0.491 \\
\bottomrule
\end{tabular}
\end{table}

Gold decomposition improves over model decomposition by +0.091 F1 on paired valid outputs (n=199, 95\% CI $[+0.041,+0.142]$) and exceeds CoT-SC by +0.075 F1 on the 200-sample comparison (95\% CI $[+0.017,+0.134]$). These are privileged-information upper bounds, not automatic-system results.

\section{Computational Cost}

Table~\ref{tab:cost} reports a legacy HotpotQA cost profile. The accuracy values use the historical truncated-context protocol and are not comparable with the full-context HotpotQA boundary result in the main paper. Backward verification is post-hoc in the evaluated single-path configuration and can be disabled when only the final answer is required.

\begin{table}[h]
\centering
\caption{Legacy truncated-context cost profile (HotpotQA, n=500).}
\label{tab:cost}
\small
\begin{tabular}{lcccc}
\toprule
Method & LLM calls/q & Latency & EM & F1 \\
\midrule
Zero-Shot & 1 & 0.7s & 0.276 & 0.389 \\
Std CoT & 1 & 3.0s & 0.264 & 0.368 \\
CoT-SC (N=3) & 3 & 8.3s & 0.262 & 0.373 \\
MoDeGraph-style & 3 & 8.7s & 0.252 & 0.366 \\
GERS-Adap. & 1--4 & 4.8s & 0.284 & 0.395 \\
GERS-SC (K=3) & $\sim$12--15 & 16.2s & 0.282 & 0.398 \\
\textbf{GERS-DAG+BiCheck} & $\sim$6--8 & 6.6s & \textbf{0.302} & \textbf{0.413} \\
\bottomrule
\end{tabular}
\end{table}

\section{Additional Diagnostics and Rejected Variants}

\textbf{Qwen-Plus diagnostic.} On HotpotQA n=300, GERS-DAG obtains EM 0.363 / F1 0.496 and CoT-SC obtains EM 0.367 / F1 0.494 (EM difference $-0.004$, McNemar $p=1.000$; F1 difference $+0.002$). Because this is outside the LongBench setting, it does not establish a general model-scaling trend.

\textbf{Weight design.} Uniform and position-weighted diagnostic scores produce similar legacy-run answers, as expected because the score is computed after answer generation.

\textbf{2Wiki at larger scale.} On 300 samples, GERS-DAG EM 0.390 / F1 0.462 remains below Standard CoT EM 0.443 / F1 0.521.

\textbf{Evidence-grounded verification (diagnostic).} We test an evidence-grounded BiCheck variant on the first 100 samples, where each backward sub-answer must quote a supporting context span and the score multiplies an evidence-grounding heuristic. On HotpotQA it preserves EM and slightly changes F1 (standard pipeline 0.451 vs.\ grounded 0.455) while lowering CS from 0.781 to 0.730. On 2Wiki it preserves EM and stays close in F1 (0.469 vs.\ 0.463), and improves bridge\_comparison F1 from 0.524 to 0.571 within the same diagnostic rerun, but loses on other types. Because this was a separate diagnostic rerun, its per-type numbers should be compared only against the same-run standard-pipeline row. Evidence grounding suppresses inflated self-consistency scores and helps some bridge cases, but is not yet a robust end-task improvement.

\textbf{Rejected variants.} Verification-driven repair raises CS while reducing EM/F1. Stepwise NLI re-answering adds only +0.004 F1 in its Oracle-decomposition test. Iterative deepening decomposition acts after the initial depth decision and fails to repair compressed decompositions. Per-sub-question BM25 retrieval is 0.121 F1 below full-context GERS-DAG on HotpotQA. These variants are reported as negative design-space evidence rather than method improvements.

\section{Implementation and Reproducibility}

\textbf{Model and API.} Qwen3-8B via DashScope (OpenAI-compatible) with \texttt{enable\_thinking=False}; Qwen-Plus for the generalization run. \textbf{Parallelism:} ThreadPoolExecutor with 4 workers (4 is the stable sweet spot; 6+ workers trigger DashScope QPM 429, handled by exponential-backoff retry at 1/2/4s on RateLimitError/APITimeoutError/APIConnectionError/InternalServerError; \texttt{max\_retries=0}, \texttt{timeout=60}). \textbf{Seeds:} bootstrap uses \texttt{numpy.random.default\_rng(42)} with $B=10000$; the result is stable across seeds 0/1/42/123/2024. \textbf{Statistics:} paired bootstrap resamples per-sample differences (not unpaired); McNemar uses chi-square with Edwards' continuity correction. Reproducer: \texttt{experiments/\_paired\_stats.py}. \textbf{Datasets:} HotpotQA and 2WikiMultiHopQA are publicly available with the cited references. \textbf{Code:} the implementation, experiment runner, figure/Word generators, and the stats reproducer are provided in the code archive accompanying this submission.

\end{document}
